### 2022-06-15 paper.tex
add leonie to ack
add alexey to ack

S.\ A.\ and L.\ P.\ M.\ K.\ acknowledge funding by the Klaus Tschira Foundation.
L.\ P.\ M.\ K., S.\ C.\ and A.\ M.-V.\ acknowledge funding from the European Commission via ERC grant 771376.

>>>>

S.\ A.\ and L.\ P.\ M.\ K.\ acknowledge funding by the Klaus Tschira Foundation.
L.\ P.\ M.\ K., L.\ K., S.\ C.\ and A.\ M.-V.\ acknowledge funding from the European Commission via ERC grant 771376.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.
